---
title: 'Blog post about price shock after review'
author: "JJayes"
date: "14/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

I want to write a trundler blog post that looks at the price of different wines over time, and then looking to see if a review from Christian Eedes translates into a price shock. 

```{r}
library(tidyverse)
wines <- read_rds("data/wines_01.rds")

```

```{r}
fairview_wines <- wines %>% 
  filter(str_detect(product, "Fairview"))
```

```{r}
fairview_wines <- fairview_wines %>% 
  mutate(prices = map(product_id, product_prices))

fairview_wines <- fairview_wines %>% 
  unnest(prices)

fairview_wines %>% 
  select(-product_id) %>% 
  unnest(prices) %>% 
  ggplot(aes(time, price_effective, colour = product)) +
  geom_point() +
  geom_line()
```

Questions I would want to answer -

1. What products change price the most number of times
2. What products have the greatest amount of spread
3. What products have the slowest price increase within a retailer's portfolio.



```{r}
wines %>% view
```



Netflorist products


```{r}
netflorist_products <- retailer_products(59)
```


```{r}
netflorist_products %>% 
  filter(str_detect(product, "roses|Roses")) %>% view
```


```{r}
valentines_products <- products(product = "valentine")

valentines_products %>% view


valentines_products_top_200 <- valentines_products %>% 
  head(200) %>% 
  mutate(prices = map(product_id, possibly(product_prices, "failed")))


valentines_products_top_200 %>% 
  select(!product_id) %>% 
  filter(prices != "failed") %>% 
  unnest(prices) %>% 
  ggplot(aes(time, price_effective, colour = product)) +
  geom_point() +
  geom_line() +
  facet_wrap(~retailer_id) +
  theme(legend.position = "none")
```


```{r}
valentines_products_top_200 %>%
  select(!product_id) %>%
  filter(
    prices != "failed",
    retailer_id != 59
  ) %>%
  unnest(prices) %>%
  # mutate(year = lubridate::year(time)) %>% count(year)
  ggplot(aes(time, price_effective, colour = product)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = ymd_hms("2021-02-14-00-00-00"), lty = 2) +
  facet_wrap(~retailer_id) +
  theme(legend.position = "none")
```

